My title

### 2024-03-11 paper/paper.qmd
new updata of finnal paper

library(tidyverse)
library(here)
library(rstanarm)
library(modelsummary)
```

@@

@@

toronto_shelters_clean |> 
 mutate(occupancy_month = month(occupancy_date, 
                                label = TRUE,
                                abbr = FALSE)) |>
  arrange(month(occupancy_date)) |>
  drop_na(occupied_rooms) |> 
  summarise(number_occupied = mean(occupied_rooms),
             .by = occupancy_month) |>
  ggplot(aes(x= occupancy_month, y = number_occupied)) + geom_point()
```

@@

>>>>

library(tidyverse)
library(here)
library(rstanarm)
library(modelsummary)
library(knitr)
library(dplyr)
library(tibble)
```

@@

```{r}
#| label: tbl-torontoo
#| tbl-cap: Shelter usage in Toronto in 2022
#| echo: false
  toronto_shelters_clean |>
  mutate(occupancy_month = month(
    occupancy_date,
    label = TRUE,
    abbr = FALSE
  )) |>
  arrange(month(occupancy_date)) |> 
  drop_na(occupied_rooms) |>
  summarise(number_occupied = mean(occupied_rooms),
            .by = occupancy_month) |>
  kable(
    col.names = c("Month", "Avg daily occupied rooms"),
    digits = 1
  )
```

@@

toronto_shelters_clean |> 
 mutate(occupancy_month = month(occupancy_date, 
                                label = TRUE,
                                abbr = FALSE)) |>
  arrange(month(occupancy_date)) |>
  drop_na(occupied_rooms) |> 
  summarise(avgs_of_rooms_occupied = mean(occupied_rooms),
             .by = occupancy_month) |>
  ggplot(aes(x= occupancy_month, y = avgs_of_rooms_occupied)) + geom_point()
```

@@

```{r}
draws <- 1000

toronto_shelters_data_first_model_rstanarm <-
  tibble(
    sigma = rep(rexp(n = draws, rate = 1), times = 16),
    beta_0 = rep(rnorm(n = draws, mean = 0, sd = 2.5), times = 16),
    beta_1 = rep(rnorm(n = draws, mean = 8, sd = 2.5), times = 16),
    five_km_time = rep(15:30, each = draws),
    occupancy_rate_rooms = occupancy_rate_rooms, 
    mu = beta_0 + beta_1 * occupancy_rate_rooms
  ) |>
  rowwise() |>
  mutate(
    capacity_actual_room = rnorm(n = 1, mean = mu, sd = sigma)
  )

toronto_shelters_data_first_model_rstanarm |>
  ggplot(aes(x = occupancy_rate_rooms, y = capacity_actual_room)) +
  geom_point(alpha = 0.1) +
  theme_classic()
```
